The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-02-28 main.tex
addressed @bsipocz's suggestions

The \astropy Project is built on a philosophy of building from the existing
Python scientific ecosystem wherever possible. Many of the enabling technologies
like \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, or \texttt{cython},
are necessary as the core underpinnings of \astropy packages.  Often this means
simply means using these packages as ``building blocks'' (E.g., the ubiquitous
use of \texttt{numpy} arrays throughout \astropypkg).  In other cases this means
wrappers around more general algorithms that make them more convenient for
astronomy use cases (E.g., the model-fitting in the \package{astropy.modeling}
subpackage discussed in \sectionname~\ref{sec:modeling}).  Sometimes these
simple wrappers evolve into more complex implementations that address
astronomically-relevant use cases the general tool does not support (E.g.,
\package{astropy.convolution}, see \sectionname~\ref{ssec:convolution}). As a
broad rule, the Project explicitly encourages re-use of code where possible.

@@

The \package{astropy.table} subpackage provides functionality for
representing and manipulating heterogeneous data. In some respects,
this is similar to \package{numpy} record arrays \citep{numpy} or
\package{pandas} data frames \citep{pandas} but with modifications for
astronomical data. Most notably, tables from \package{astropy.table}
allow for table or column metadata and can handle
vectors/arrays or arbitrary objects (with suitable column-like characteristics)
as table entries. The subpackage was described in
detail in \cite{astropy}.  Thus, in what follows, we only summarize
key new features or updates to \package{astropy.table} since the
previous \astropy paper. These are support for grouped table
operations, table concatenation, and using array-valued
\package{astropy} objects as table columns.

@@

Additionally, there is now interoperability between \texttt{Table}
objects and \package{pandas} data frames using the \texttt{Table.to_pandas()}
and \texttt{Table.from_pandas()} methods. \texttt{Table.to_pandas()} is,
however, limited to a subset of possible \texttt{Table} objects, because several
of the features outlined above cannot be represented as \package{pandas} data
frames. While these features might be contributed to or combined with
\package{pandas} at a later date, the architectural differences that
enable these areas are significant, so no one has yet volunteered to do this
major undertaking.

>>>>

The \astropy Project is built on a philosophy of building from the existing
Python scientific ecosystem wherever possible. Many of the enabling technologies
like \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, or \texttt{cython},
are necessary as the core underpinnings of \astropy packages.  Often this means
using these packages as ``building blocks'' (E.g., the ubiquitous
use of \texttt{numpy} arrays throughout \astropypkg).  In other cases this means
wrappers around more general algorithms that make them more convenient for
astronomy use cases (E.g., the model-fitting in the \package{astropy.modeling}
subpackage discussed in \sectionname~\ref{sec:modeling}).  Sometimes these
simple wrappers evolve into more complex implementations that address
astronomically-relevant use cases the general tool does not support (E.g.,
\package{astropy.convolution}, see \sectionname~\ref{ssec:convolution}). As a
broad rule, the Project explicitly encourages re-use of code where possible.

@@

The \package{astropy.table} subpackage provides functionality for
representing and manipulating heterogeneous data. In some respects,
this is similar to \package{numpy} record arrays \citep{numpy} or
\package{pandas} \texttt{DataFrame} objects \citep{pandas}, but with modifications for
astronomical data. Most notably, tables from \package{astropy.table}
allow for table or column metadata and can handle
vectors/arrays or arbitrary objects (with suitable column-like characteristics)
as table entries. The subpackage was described in
detail in \cite{astropy}.  Thus, in what follows, we only summarize
key new features or updates to \package{astropy.table} since the
previous \astropy paper. These are support for grouped table
operations, table concatenation, and using array-valued
\package{astropy} objects as table columns.

@@

Additionally, there is now interoperability between \texttt{Table}
and \package{pandas} \texttt{DataFrame} objects using the \texttt{Table.to_pandas()}
and \texttt{Table.from_pandas()} methods. \texttt{Table.to_pandas()} is,
however, limited to a subset of possible \texttt{Table} objects, because several
of the features outlined above cannot be represented as \package{pandas} data
frames. While these features might be contributed to or combined with
\package{pandas} at a later date, the architectural differences that
enable these areas are significant, so no one has yet volunteered to do this
major undertaking.
